### 2020-05-31 writeup/transfer.tex
add procedure

\textbf{Algorithmic consequence.} \todo{}

\subsection{Covariate Shift}

>>>>

\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that the $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho$.
Instead, from the analysis, we observe that $L(\hat{\beta}_t^{\MTL})$ is quadratic.
Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
Algorithm \ref{alg_inc_train} shows the procedure.

\begin{algorithm}[!t]
	\caption{An incremental training schedule for multi-task learning}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\State as
	\end{algorithmic}
\end{algorithm}
\subsection{Covariate Shift}
